The process of retrieving schedule data from the Novasoftware web application

### 2016-04-19 paper/paper.tex
Made the page wrap a litte bit better on some pages

		while(parts.length) {
			var course = parts.shift();
			var unknowns = [];
			while(parts[0] && isUnknown(parts[0])) {
				unknowns.push(parts.shift());
			}
			var teacher = null;
			if(parts[0] && isTeacher(parts[0])) {
				teacher = parts.shift();
			}
			var location = null;
			if(parts[0] && isLocation(parts[0])) {
				location = parts.shift();
			}
			details.push({
				course: course,
				unknowns: unknowns,
				teacher: teacher,
				location: location
			});
		}

@@

	\begin{lstlisting}[language=HTTP, style=nonumbers]
	GET
	http://www.novasoftware.se/ImgGen/schedulegenerator.aspx
	query: {
		schoolid: {schoolId}
		id: {classId}
		week: {week}
		format: png
		period: null
		width: 1
		height: 1
	}
	\end{lstlisting}

>>>>

		while(parts.length) {
			var course = parts.shift();
			var unknowns = [];

			while(parts[0] && isUnknown(parts[0])) {
				unknowns.push(parts.shift());
			}
			var teacher = null;
			if(parts[0] && isTeacher(parts[0])) {
				teacher = parts.shift();
			}
			var location = null;
			if(parts[0] && isLocation(parts[0])) {
				location = parts.shift();
			}
			details.push({
				course: course,
				unknowns: unknowns,
				teacher: teacher,
				location: location
			});
		}

@@

	\newpage
	\begin{lstlisting}[language=HTTP, style=nonumbers]
	GET
	http://www.novasoftware.se/ImgGen/schedulegenerator.aspx
	query: {
		schoolid: {schoolId}
		id: {classId}
		week: {week}
		format: png
		period: null
		width: 1
		height: 1
	}
	\end{lstlisting}
